NumPy---Array Programming in Python

### 2020-02-10 paper.tex
Feedback from Paul and Ross
Update Fig. 2

We thank Ross Barnowski, Michael Eickenberg, and Perry Greenfield, who
suggested text and provided helpful feedback on the manuscript.

@@

Jim Hugunin wrote Numeric in 1995, while a graduate student at MIT.
Hugunin based his package on previous work by Jim Fulton, then working at the
US Geological Survey, with input from many others.
After he graduated, Paul Dubois at the Lawrence Livermore National Laboratory
became the maintainer.
Many people contributed to the project including Travis Oliphant (a co-author
of this paper), David Ascher, Tim Peters, and Konrad Hinsen.

>>>>

We thank Ross Barnowski, Paul Dubois, Michael Eickenberg, and Perry Greenfield, who
suggested text and provided helpful feedback on the manuscript.

@@

Jim Hugunin wrote Numeric in 1995, while a graduate student at MIT.
Hugunin based his package on previous work by Jim Fulton, then working at the
US Geological Survey, with input from many others.
After he graduated, Paul Dubois at the Lawrence Livermore National Laboratory
became the maintainer.
Many people contributed to the project including T.E.O. (a co-author
of this paper), David Ascher, Tim Peters, and Konrad Hinsen.
